Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-04-03 paper/tv.tex
m

>>>>

\begin{figure}[ht]
  \vspace{0mm}
\begin{lstlisting}[columns=fullflexible]
var x := -1; 
var ct := 0;

void process (int i)
/* requires d1<d2,  emp 
   ensures  true, (Update(i)#d1.emp#d2.([x=i]Critical(i).Exit(i) \/ emp))^* */
{
  [x=-1] active (i, 2, 3); 
  deadline (event[Update(i)]{x := i}, d1);
  delay (d2);
  if (x=i) {
    event[Critical(i)]{ct := ct +1};
    event[Exit(i)]{ct := ct -1; x := -1};
    process (i);
  } else {
    process (i);
}

void main () 
/* requires true /\ emp 
   ensures  true, (!Critical \/ (Critical(i) /\ i=x))^* */
{ process(0) || process(1) || process(2); }
\end{lstlisting}  
  \vspace{0mm}
  \caption{Dependent Values for Time Bounds).}\label{fig:overview_ficher}
     \vspace{0mm}
\end{figure}
